---
title: "hw1"
author: "Jiayu Liu"
date: "5/24/2022"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(dplyr)
rm(list = ls())
```



Problem 1
```{r cars}
housing <- read_csv("NYChousing.csv")
dim(housing)
```
There are 22 cloumns and 2506 rows in this dataset.

```{r}
colnames(housing)
```

```{r}
ls(housing)
```

4. The apply function counts how many NA in each columns. 
```{r}
apply(is.na(housing), 2, sum)


```

```{r}
housing1 <- housing %>% drop_na(Value)
dim(housing1)


```
5. I have removed 2506 - 2454 = 52  rows from the original file. Yes, it agrees with part 4.

6. 
```{r}
quantile(housing1$Value)
```
75% is 2684851.

```{r}
housing1$HighValue <- ifelse(housing1$Value > 2684851, "High", "NotHigh")
housing1
```
9.
```{r}
table(housing1$HighValue,housing1$Borough)

```


10.
```{r}
housing1 %>% count(HighValue)
cat('Proportion is ', 137/(614+1840))
#condition mean
mean(housing1$HighValue == "High" & housing1$Borough == "Bronx")
```
11. Conditional Probability P(A|B) = P(AB)/P(B)
```{r}
cat('The probability is', 0.05582722/((137+527)/(614+1840)))

#2nd method
mean(housing1$HighValue == "High" & housing1$Borough == "Bronx")/mean(housing1$Borough == "Bronx")

```

12.
```{r}
logValue <- log(housing1$Value)
housing1 <- cbind(housing1,logValue)
cat("min",min(housing1$logValue),"median",median(housing1$logValue),"mean",mean(housing1$logValue),"max",max(housing1$logValue))
```

13.
```{r}
logUnits <- log(housing1$UnitCount)
housing1 <- cbind(housing1,logUnits)
```

14.
```{r}
housing1$after1950 <- ifelse(housing1$YearBuilt > 1950, "True", "False")

```

Part2

1.
```{r}
boxplot(housing1$Value ~ housing1$Borough,
        main = "boxplot",
        ylab = "Value",
        xlab = "Borough"
        
        
        
        )


boxplot(housing1$logValue ~ housing1$Borough,
        main = "boxplot",
        ylab = "Log Value",
        xlab = "Borough"
        
        
        
        )
```
2.
```{r}
plot(logUnits,housing1$logValue,xlab="Log Units",ylab="Log Value")

```

3.
The trend is that there is a positve relation with value and built after 1950, also there is a positive relation with units and built after 1950. We can conclude that after 1950, the houses have more value and more units. 
```{r}
plot(logUnits,housing1$logValue, 
     ylab = "logValue", 
     xlab = "logUnits", 
     col = factor(housing1$after1950))
legend("bottomright", legend = levels(factor(housing1$after1950)), fill
= unique(factor(housing1$after1950)))
```

4.

```{r}
i = cor(logUnits,housing1$logValue)
print(i)
Man_Logunits <- subset(housing1$logUnits,housing1$Borough == "Manhattan")
Man_LogValue <- subset(housing1$logValue,housing1$Borough == "Manhattan")

ii = cor(Man_Logunits,Man_LogValue)
print(ii)
```
```{r}
cor(housing1[housing1$Borough == "Brooklyn",]$logUnits,housing1[housing1$Borough == "Brooklyn",]$logValue )
```
```{r}
cor(housing1[housing1$after1950 == "True",]$logUnits,housing1[housing1$after1950 == "True",]$logValue )
```
```{r}
cor(housing1[housing1$after1950 == "False",]$logUnits,housing1[housing1$after1950 == "False",]$logValue )
```

5.
```{r}
library(ggplot2)


```


```{r}
data_new1 <- subset(housing1,housing1$Borough == "Brooklyn")
data_new2 <- subset(housing1,housing1$Borough == "Manhattan")

data_new3 <- rbind(data_new1,data_new2)




```

```{r}
ggplot(data=data_new3, aes(x=logUnits, y=logValue, color=Borough))+geom_point(size=3)
```

6.
```{r}
median(subset(housing1,housing1$Borough =="Manhattan")$Value,na.rm = "True")
```

7.
```{r}
median(subset(housing1,housing1$Borough =="Manhattan")$Value,na.rm = "True")
median(subset(housing1,housing1$Borough =="Brooklyn")$Value,na.rm = "True")
median(subset(housing1,housing1$Borough =="Bronx")$Value,na.rm = "True")
median(subset(housing1,housing1$Borough =="Queens")$Value,na.rm = "True")
median(subset(housing1,housing1$Borough =="Staten Island")$Value,na.rm = "True")
```

