---
title: "hw3"
author: "Jiayu Liu"
date: '2022-06-21'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(plyr)
library(tidyverse)
```



```{r cars}
debt <- read.csv("debt.csv", as.is = TRUE)
```



```{r pressure, echo=FALSE}
mean.growth <- function(country.df){
  return(mean(country.df$growth))
}
```

```{r}
daply(debt,
      .(Country),
      mean.growth)
```

```{r}
growth_y <- daply(debt,
                  .(Year),
                  mean.growth)
year <- seq(1947,2010,by=1)
plot(year,growth_y,sty="l",ylab='mean growth',type='l')
```
### 3
```{r}
signif(cor(debt$growth,debt$ratio),3)
```
```{r}
correlation <- function(df){
  return(cor(df$growth,df$ratio))
}

correla <- daply(debt,
      .(Country),
      correlation
      )
correla
signif(mean(correla),3)
hist(correla,breaks=10)
```
### c
```{r}
mean_year <- daply(debt,
      .(Year),
      correlation)
mean_year
hist(mean_year,breaks=10, xlab='year')
mean(mean_year)
```
### 3d
```{r}
larger0 <- function(df1){
  return(df1>0)



  }
aaply(correla,1,larger0)
table(aaply(correla,1,larger0))
unlist(lapply(aaply(correla,1,larger0), function(x) x[isTRUE(x)]))

```
From the data above, we can tell that there is a negative correlation between GDP growth and debt. As we can see there are 6 countries going against general trend.
```{r}
aaply(mean_year,1,larger0)
table(aaply(mean_year,1,larger0))
unlist(lapply(aaply(mean_year,1,larger0), function(x) x[isTRUE(x)]))
```
### There are 15 years going against the trend.


## 4
```{r}
fitline <- lm(growth~ratio, debt)
summary(fitline)
```
The intercept is roughly 4.28 and beta1 is -0.0183.
```{r}
plot(debt$growth~debt$ratio)
abline(lm(debt$growth~debt$ratio), col="red")
```
### 5
```{r}
correla[correla < -0.5]
```
```{r}
par(mfrow=c(2,2))

plot(growth~ratio, data = debt[debt$Country=="France",],
     main = "France")
abline(lm(growth~ratio, data = debt[debt$Country=="France",]), col="red")

plot(growth~ratio, data = debt[debt$Country=="Germany",],
     main = "Germany")
abline(lm(growth~ratio, data = debt[debt$Country=="Germany",]), col="blue")

plot(growth~ratio, data = debt[debt$Country=="Italy",],
     main = "Italy")
abline(lm(growth~ratio, data = debt[debt$Country=="Italy",]), col="red")

plot(growth~ratio, data = debt[debt$Country=="Japan",],
     main = "Japan")
abline(lm(growth~ratio, data = debt[debt$Country=="Japan",]), col="blue")
```
### 6a
```{r}


France.new <- filter(debt,Country == 'France')
dim(France.new)
```
```{r}
France.new$next.growth <- NA

for (i in 1:(nrow(France.new)-1)){
if (France.new$Year[i+1]==France.new$Year[i]+1){
  France.new$next.growth[i] = France.new$growth[i+1]
  } 
  else
    {France.new$next.growth[i] = NA}
  }
France.new
France.new[France.new$Year == 1971,]
France.new[France.new$Year == 1972,]
```
### 7
```{r}
debt$next.growth <- NA


next.g <- function(country.df){
for (i in 1:(nrow(country.df)-1)){
if (country.df$Year[i+1]==country.df$Year[i]+1){
  country.df$next.growth[i] = country.df$growth[i+1]
  } 
  else
  {country.df$next.growth[i] = NA}
  
}
  return(country.df)
}

whole_data <- ddply(debt,
      .(Country),
      next.g)



filter(whole_data,Country == "France" & Year == 2009)

```
### 8
```{r}
line_r <- lm(whole_data$next.growth~whole_data$ratio)

summary(line_r)
plot(whole_data$next.growth~whole_data$ratio)
abline(line_r, col="red")
```
### the slope from the summary table is -0.0116 and the intercept is 3.924. By comparing with the previous graph, the relation between ratio and growth is weak. There is not much difference between two graphs.


### 9
```{r}
linen <- lm(whole_data$next.growth~whole_data$growth) 
plot(whole_data$next.growth~whole_data$growth)
abline(linen, col="red")
summary(linen)
```
The intercept is 1.97 and slope is 0.4. From the graph we can tell that there is a stronger relation between current year and next year than growth and ratio.
